---
title: "Who is the winner?"
author: "Khuong Le"
date: "23/5/2018"
output: html_document
---

This Rmarkddown is used to predict matches in knock out stage to semifinals, third place match and final. 

```{r}
pkg_list = c("ggplot2", "stringr", "rvest", "tidyr", "dplyr", "base","scales","plyr", "reshape2")
mia_pkgs = pkg_list[!(pkg_list %in% installed.packages()[,"Package"])]
if(length(mia_pkgs) > 0) install.packages(mia_pkgs)
loaded_pkgs = lapply(pkg_list, require, character.only=TRUE)
```

According to the knockout_phase document. Compare 3 of the following requirements: 1st position, second position and chance qualify. Have 2 out of 3 better means that teams can qualifiy.
```{r}
world_data = read.csv("worldcup_data.csv")
kophase    = read.csv("ko.csv")
```


Goals for each team. 
```{r}
set.seed(1602)
ko_goals = function(avggs1, avghis1, avggc2){
  result = 0
  avgscore = (avggs1  + avghis1)/2
  oppconcd = (avgscore + avggc2)/2
  prob = (avgscore + oppconcd)/4
  result = round(avgscore) + rbinom(1,2,prob)
  return (result)
}
```


Functions for the score in knock-out stage.

```{r}
set.seed(2405)
kophasegoals = function(name1, avggs1, avggc1, avghis1, name2, avggs2, avggc2, avghis2){
  result = vector(mode = "numeric", length = 8)
  goalteam1 = ko_goals(avggs1, avghis1, avggc2) 
  goalteam2 = ko_goals(avggs2, avghis2, avggc1)
  j = 1
  k = 1
  penteam1  = vector(mode = "numeric", length = j)
  penteam2  = vector(mode = "numeric", length = k)
  
  result[1] = name1
  result[2] = sum(goalteam1)
  result[3] = sum(goalteam2)
  result[4] = name2
  
  if(result[2] > result[3]){
      result[5] = "No penalty"
      result[6] = 0
      result[7] = 0
      result[8] = name1
  }

  else if(result[2] < result[3]){ 
    result[5] = "No penalty"
    result[6] = 0
    result[7] = 0
    result[8] = name2
  }
  else if (result[2] == result[3]){
    result[5] = "Penalty"
    for(i in 1:100){
      penteam1[j] = rbinom(1,1,0.5)
      penteam2[k] = rbinom(1,1,0.5)
      j = j + 1
      k = k + 1
      if((sum(penteam1) >=4 || sum(penteam2) >= 3) && abs(sum(penteam1) - sum(penteam2)) == 2) { 
        result[6] = sum(penteam1)
        result[7] = sum(penteam2)
        break
      }
    }
    if(result[6] > result[7]){  result[8] = name1  }
    else{ result[8] = name2  }
  }
  
  return(result)
}
```



Play each match in the ko out stage 1000 times and find the average for the result.
```{r}
#Left brackets
# > 80%    : winner round up, loser round down (if < 0.85) (no penalty)
# 60 - 80% : no decimal (no penalty)
# 50 - 60% : round both team. (penalty)
# 49: 1C vs 2D (France - Croatia)
# 50: 1A vs 2B (Uruguay - Portugal)
# 51: 1B vs 2A (Spain - Russia)
# 52: 1D vs 2C (Argentina - Denmark)
```

Left brackets

Head to head record is from this website : https://www.11v11.com/teams/france/tab/opposingTeams/opposition/Croatia/

First match:
```{r}
set.seed(1602)
n = 1000
# 1C vs 2D (France - Croatia)
fra_gs = round(sum(kophase$teamC1_gs[which(kophase$teamC1 == "France")])/(length(kophase$teamC1[which((kophase$teamC1 == "France"))])*6),2)
fra_gc = round(sum(kophase$teamC1_gc[which(kophase$teamC1 == "France")])/(length(kophase$teamC1[which((kophase$teamC1 == "France"))])*6),2)
cro_gs = round(sum(kophase$teamD2_gs[which(kophase$teamD2 == "Croatia")])/(length(kophase$teamD2[which((kophase$teamD2 == "Croatia"))])*6),2)
cro_gc = round(sum(kophase$teamD2_gc[which(kophase$teamD2 == "Croatia")])/(length(kophase$teamD2[which((kophase$teamD2 == "Croatia"))])*6),2)
match49 = data.frame(team1 = c("France"), team2 = c("Croatia"), played = c(5), fraW = c(3), draw = c(2), croW = c(0), FRA_gs = c(9), CRO_gs = c(3),
                      avggfra_gs = c(fra_gs), avggfra_gc = c(fra_gc), avggcro_gs = c(cro_gs), avggcro_gc = c(cro_gc))
#france gs = cro_gc
avghisfra = match49$FRA_gs / match49$played
avghiscro = match49$CRO_gs / match49$played

resmatch49 = NULL
for(i in 1:n){
resmatch49[i] = list(kophasegoals(as.character(match49$team1), match49$avggfra_gs, match49$avggfra_gc, avghisfra, as.character(match49$team2), match49$avggcro_gs, match49$avggcro_gc, avghiscro))
}
```

Analyze match 49

```{r}
france_win_per  = 0
france_gs = 0
croatia_win_per = 0
croatia_gs = 0
for(i in 1:n){
  if(resmatch49[[i]][8] == "France"){ france_win_per = france_win_per + 1 }
  else{ croatia_win_per = croatia_win_per + 1 }
  france_gs  = france_gs  + as.numeric(resmatch49[[i]][2])
  croatia_gs = croatia_gs + as.numeric(resmatch49[[i]][3])
}
france_win_per/n * 100
round(france_gs / n,2)
croatia_win_per/n * 100
round(croatia_gs / n,2)
```

France 3 - 1 Croatia 

Second match:
```{r}
set.seed(1602)
# 1A vs 2B (Uruguay - Portugal)
uru_gs = round(sum(kophase$teamA1_gs[which(kophase$teamA1 == "Uruguay")])/(length(kophase$teamA1[which((kophase$teamA1 == "Uruguay"))])*6),2)
uru_gc = round(sum(kophase$teamA1_gc[which(kophase$teamA1 == "Uruguay")])/(length(kophase$teamA1[which((kophase$teamA1 == "Uruguay"))])*6),2)
por_gs = round(sum(kophase$teamB2_gs[which(kophase$teamB2 == "Portugal")])/(length(kophase$teamB2[which((kophase$teamB2 == "Portugal"))])*6),2)
por_gc = round(sum(kophase$teamB2_gc[which(kophase$teamB2 == "Portugal")])/(length(kophase$teamB2[which((kophase$teamB2 == "Portugal"))])*6),2)
match50 = data.frame(team1 = c("Uruguay"), team2 = c("Portugal"), played = c(2), uruW = c(0), draw = c(1), porW = c(1), URU_gs = c(1), POR_gs = c(4),
                      avgguru_gs = c(uru_gs), avgguru_gc = c(uru_gc), avggpor_gs = c(por_gs), avggpor_gc = c(por_gc))

#uruguay gs = por_gc
avghisuru = match50$URU_gs / match50$played
avghispor = match50$POR_gs / match50$played

resmatch50 = NULL
for(i in 1:n){
resmatch50[i] = list(kophasegoals(as.character(match50$team1), match50$avgguru_gs, match50$avgguru_gc, avghisuru, as.character(match50$team2), match50$avggpor_gs, match50$avggpor_gc, avghispor))
}
```

Analyze match 50

```{r}
portugal_win_per  = 0
portugal_gs = 0
uruguay_win_per = 0
uruguay_gs = 0
for(i in 1:n){
  if(resmatch50[[i]][8] == "Portugal"){ portugal_win_per = portugal_win_per + 1 }
  else{ uruguay_win_per = uruguay_win_per + 1 }
  uruguay_gs   = uruguay_gs   + as.numeric(resmatch50[[i]][2])
  portugal_gs  = portugal_gs  + as.numeric(resmatch50[[i]][3])
}
uruguay_win_per/n * 100
round(uruguay_gs / n, 2)
portugal_win_per/n * 100
round(portugal_gs / n,2)

```

Uruguay 1 - 2 Portugal 

Third match:
```{r}
# 1B vs 2A (Spain - Russia)
set.seed(1602)
esp_gs = round(sum(kophase$teamB1_gs[which(kophase$teamB1 == "Spain")])/(length(kophase$teamB1[which((kophase$teamB1 == "Spain"))])*6),2)
esp_gc = round(sum(kophase$teamB1_gc[which(kophase$teamB1 == "Spain")])/(length(kophase$teamB1[which((kophase$teamB1 == "Spain"))])*6),2)
rus_gs = round(sum(kophase$teamA2_gs[which(kophase$teamA2 == "Russia")])/(length(kophase$teamA2[which((kophase$teamA2 == "Russia"))])*6),2)
rus_gc = round(sum(kophase$teamA2_gc[which(kophase$teamA2 == "Russia")])/(length(kophase$teamA2[which((kophase$teamA2 == "Russia"))])*6),2)
match51 = data.frame(team1 = c("Spain"), team2 = c("Russia"), played = c(6), espW = c(4), draw = c(2), rusW = c(0), ESP_gs = c(12), RUS_gs = c(6),
                      avggesp_gs = c(esp_gs), avggesp_gc = c(esp_gc), avggrus_gs = c(rus_gs), avggrus_gc = c(rus_gc))

#Spain gs = Russia gc
avghisesp = match51$ESP_gs / match51$played
avghisrus = match51$RUS_gs / match51$played

resmatch51 = NULL
for(i in 1:n){
resmatch51[i] = list(kophasegoals(as.character(match51$team1), match51$avggesp_gs, match51$avggesp_gc, avghisesp, as.character(match51$team2), match51$avggrus_gs, match51$avggrus_gc, avghisrus))
}
```

Analyze match 51

```{r}
spain_win_per  = 0
spain_gs = 0
russia_win_per = 0
russia_gs = 0
for(i in 1:n){
  if(resmatch51[[i]][8] == "Spain"){ spain_win_per = spain_win_per + 1 }
  else{ russia_win_per = russia_win_per + 1 }
  spain_gs  = spain_gs  + as.numeric(resmatch51[[i]][2])
  russia_gs = russia_gs + as.numeric(resmatch51[[i]][3])
}
spain_win_per/n * 100
round(spain_gs / n,2)
russia_win_per/n * 100
round(russia_gs / n, 2)
```

Spain 4 - 2 Russia 

Fourth match:
```{r}
# 1D vs 2C (Argentina - Denmark)
set.seed(1602)
arg_gs = round(sum(kophase$teamD1_gs[which(kophase$teamD1 == "Argentina")])/(length(kophase$teamD1[which((kophase$teamD1 == "Argentina"))])*6),2)
arg_gc = round(sum(kophase$teamD1_gc[which(kophase$teamD1 == "Argentina")])/(length(kophase$teamD1[which((kophase$teamD1 == "Argentina"))])*6),2)
dan_gs = round(sum(kophase$teamC2_gs[which(kophase$teamC2 == "Denmark")])/(length(kophase$teamC2[which((kophase$teamC2 == "Denmark"))])*6),2)
dan_gc = round(sum(kophase$teamC2_gc[which(kophase$teamC2 == "Denmark")])/(length(kophase$teamC2[which((kophase$teamC2 == "Denmark"))])*6),2)
match52 = data.frame(team1 = c("Argentina"), team2 = c("Denmark"), played = c(3), argW = c(2), draw = c(0), denW = c(1), ARG_gs = c(4), DAN_gs = c(3),
                      avggarg_gs = c(arg_gs), avggarg_gc = c(arg_gc), avggdan_gs = c(dan_gs), avggdan_gc = c(dan_gc))

#Argentina gs = Denmark gc
avghisarg = match52$ARG_gs / match52$played
avghisdan = match52$DAN_gs / match52$played

resmatch52 = NULL
for(i in 1:n){
resmatch52[i] = list(kophasegoals(as.character(match52$team1), match52$avggarg_gs, match52$avggarg_gc, avghisarg, as.character(match52$team2), match52$avggdan_gs, match52$avggdan_gc, avghisdan))
}
```

Analyze match 52

```{r}
argentina_win_per  = 0
argentina_gs = 0
denmark_win_per = 0
denmark_gs = 0

for(i in 1:n){
  if(resmatch52[[i]][8] == "Argentina"){ argentina_win_per = argentina_win_per + 1 }
  else{ denmark_win_per = denmark_win_per + 1 }
  argentina_gs  = argentina_gs  + as.numeric(resmatch52[[i]][2])
  denmark_gs = denmark_gs + as.numeric(resmatch52[[i]][3])
}
argentina_win_per/n * 100
round(argentina_gs / n,2)
denmark_win_per/n * 100
round(denmark_gs / n, 2)
```

Argentina 2 - 2 Denmark (Argentina win penalty)

```{r}
#Right brackets
# > 80%    : winner round up, loser round down (if < .85) (no penalty)
# 60 - 80% : no decimal (no penalty)
# 50 - 60% : round both team. (penalty)
# 53: 1E vs 2F (Brazil - Mexico)
# 54: 1G vs 2H (Belgium - Colombia)
# 55: 1F vs 2E (Germany - Switzerland)
# 56: 1H vs 2G (Poland - England)
```

First match
```{r}
# 1E vs 2F (Brazil - Mexico)
set.seed(1602)
bra_gs = round(sum(kophase$teamE1_gs[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
bra_gc = round(sum(kophase$teamE1_gc[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
mex_gs = round(sum(kophase$teamF2_gs[which(kophase$teamF2 == "Mexico")])/(length(kophase$teamF2[which((kophase$teamF2 == "Mexico"))])*6),2)
mex_gc = round(sum(kophase$teamF2_gc[which(kophase$teamF2 == "Mexico")])/(length(kophase$teamF2[which((kophase$teamF2 == "Mexico"))])*6),2)
match53 = data.frame(team1 = c("Brazil"), team2 = c("Mexico"), played = c(40), bragW = c(23), draw = c(7), mexW = c(10), BRA_gs = c(73), MEX_gs = c(36),
                      avggbra_gs = c(bra_gs), avggbra_gc = c(bra_gc), avggmex_gs = c(mex_gs), avggmex_gc = c(mex_gc))

#Brazil gs = Mexico gc
avghisbra = match53$BRA_gs / match53$played
avghismex = match53$MEX_gs / match53$played

resmatch53 = NULL
for(i in 1:n){
resmatch53[i] = list(kophasegoals(as.character(match53$team1), match53$avggbra_gs, match53$avggbra_gc, avghisbra, as.character(match53$team2), match53$avggmex_gs, match53$avggmex_gc, avghismex))
}
```

Analyze match 53

```{r}
brazil_win_per  = 0
brazil_gs = 0
mexico_win_per = 0
mexico_gs = 0

for(i in 1:n){
  if(resmatch53[[i]][8] == "Brazil"){ brazil_win_per = brazil_win_per + 1 }
  else{ mexico_win_per = mexico_win_per + 1 }
  brazil_gs = brazil_gs  + as.numeric(resmatch53[[i]][2])
  mexico_gs = mexico_gs + as.numeric(resmatch53[[i]][3])
}
brazil_win_per/n * 100
round(brazil_gs / n,2)
mexico_win_per/n * 100
round(mexico_gs / n, 2)
```

Brazil 4 - 1 Mexico

Second match
```{r}
#1G vs 2H (Belgium - Colombia)
set.seed(1602)
bel_gs = round(sum(kophase$teamG1_gs[which(kophase$teamG1 == "Belgium")])/(length(kophase$teamG1[which((kophase$teamG1 == "Belgium"))])*6),2)
bel_gc = round(sum(kophase$teamG1_gc[which(kophase$teamG1 == "Belgium")])/(length(kophase$teamG1[which((kophase$teamG1 == "Belgium"))])*6),2)
col_gs = round(sum(kophase$teamH2_gs[which(kophase$teamH2 == "Colombia")])/(length(kophase$teamH2[which((kophase$teamH2 == "Colombia"))])*6),2)
col_gc = round(sum(kophase$teamH2_gc[which(kophase$teamH2 == "Colombia")])/(length(kophase$teamH2[which((kophase$teamH2 == "Colombia"))])*6),2)
match54 = data.frame(team1 = c("Belgium"), team2 = c("Colombia"), played = c(2), belgW = c(1), draw = c(0), colW = c(1), BEL_gs = c(2), COL_gs = c(2),
                      avggbel_gs = c(bel_gs), avggbel_gc = c(bel_gc), avggcol_gs = c(col_gs), avggcol_gc = c(col_gc))

#Belgium gs = Colombia gc
avghisbel = match54$BEL_gs / match54$played
avghiscol = match54$COL_gs / match54$played

resmatch54 = NULL
for(i in 1:n){
resmatch54[i] = list(kophasegoals(as.character(match54$team1), match54$avggbel_gs, match54$avggbel_gc, avghisbel, as.character(match54$team2), match54$avggcol_gs, match54$avggcol_gc, avghiscol))
}
```

Analyze match 54

```{r}
belgium_win_per  = 0
belgium_gs = 0
colombia_win_per = 0
colombia_gs = 0

for(i in 1:n){
  if(resmatch54[[i]][8] == "Belgium"){ belgium_win_per = belgium_win_per + 1 }
  else{ colombia_win_per = colombia_win_per + 1 }
  belgium_gs  = belgium_gs  + as.numeric(resmatch54[[i]][2])
  colombia_gs = colombia_gs + as.numeric(resmatch54[[i]][3])
}
belgium_win_per/n * 100
round(belgium_gs / n,2)
colombia_win_per/n * 100
round(colombia_gs / n, 2)
```

Belgium 2 - 2 Colombia (Belgium win penalty)

Third match

```{r}
#1F vs 2E (Germany - Switzerland)
set.seed(1602)
ger_gs = round(sum(kophase$teamF1_gs[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)
ger_gc = round(sum(kophase$teamF1_gc[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)
swi_gs = round(sum(kophase$teamE2_gs[which(kophase$teamE2 == "Switzerland")])/(length(kophase$teamE2[which((kophase$teamE2 == "Switzerland"))])*6),2)
swi_gc = round(sum(kophase$teamE2_gc[which(kophase$teamE2 == "Switzerland")])/(length(kophase$teamE2[which((kophase$teamE2 == "Switzerland"))])*6),2)
match55 = data.frame(team1 = c("Germany"), team2 = c("Switzerland"), played = c(50), gergW = c(35), draw = c(6), swiW = c(9), GER_gs = c(134), SWI_gs = c(65),
                      avggger_gs = c(ger_gs), avggger_gc = c(ger_gc), avggswi_gs = c(swi_gs), avggswi_gc = c(swi_gc))

#Belgium gs = Colombia gc
avghisger = match55$GER_gs / match55$played
avghisswi = match55$SWI_gs / match55$played

resmatch55 = NULL
for(i in 1:n){
resmatch55[i] = list(kophasegoals(as.character(match55$team1), match55$avggger_gs, match55$avggger_gc, avghisger, as.character(match55$team2), match55$avggswi_gs, match55$avggswi_gc, avghisswi))
}
```

Analyze match 55

```{r}
germany_win_per  = 0
germany_gs = 0
switzerland_win_per = 0
switzerland_gs = 0

for(i in 1:n){
  if(resmatch55[[i]][8] == "Germany"){ germany_win_per = germany_win_per + 1 }
  else{ switzerland_win_per = switzerland_win_per + 1 }
  germany_gs  = germany_gs  + as.numeric(resmatch55[[i]][2])
  switzerland_gs = switzerland_gs + as.numeric(resmatch55[[i]][3])
}
germany_win_per/n * 100
round(germany_gs / n,2)
switzerland_win_per/n * 100
round(switzerland_gs / n, 2)
```

Germany 4 - 2 Switzerland

Fourth match

```{r}
#1H vs 2G (Poland - England)
set.seed(1602)
pol_gs = round(sum(kophase$teamH1_gs[which(kophase$teamH1 == "Poland")])/(length(kophase$teamH1[which((kophase$teamH1 == "Poland"))])*6),2)
pol_gc = round(sum(kophase$teamH1_gc[which(kophase$teamH1 == "Poland")])/(length(kophase$teamH1[which((kophase$teamH1 == "Poland"))])*6),2)
eng_gs = round(sum(kophase$teamG2_gs[which(kophase$teamG2 == "England")])/(length(kophase$teamG2[which((kophase$teamG2 == "England"))])*6),2)
eng_gc = round(sum(kophase$teamG2_gc[which(kophase$teamG2 == "England")])/(length(kophase$teamG2[which((kophase$teamG2 == "England"))])*6),2)
match56 = data.frame(team1 = c("Poland"), team2 = c("England"), played = c(19), polW = c(1), draw = c(7), engW = c(11), POL_gs = c(11), ENG_gs = c(30),
                      avggpol_gs = c(pol_gs), avggpol_gc = c(pol_gc), avggeng_gs = c(eng_gs), avggeng_gc = c(eng_gc))

#Belgium gs = Colombia gc
avghispol = match56$POL_gs / match56$played
avghiseng = match56$ENG_gs / match56$played

resmatch56 = NULL
for(i in 1:n){
resmatch56[i] = list(kophasegoals(as.character(match56$team1), match56$avggpol_gs, match56$avggpol_gc, avghispol, as.character(match56$team2), match56$avggeng_gs, match56$avggeng_gc, avghiseng))
}
```

Analyze match 56

```{r}
poland_win_per  = 0
poland_gs = 0
england_win_per = 0
england_gs = 0

for(i in 1:n){
  if(resmatch56[[i]][8] == "Poland"){ poland_win_per = poland_win_per + 1 }
  else{ england_win_per = england_win_per + 1 }
  poland_gs  = poland_gs  + as.numeric(resmatch56[[i]][2])
  england_gs = england_gs + as.numeric(resmatch56[[i]][3])
}
poland_win_per/n * 100
round(poland_gs / n,2)
england_win_per/n * 100
round(england_gs / n, 2)
```

Poland 1 - 2 England

Play each match in games from quaterfinals to finals 5000 times and find the average for the result.
Don't count match before 1920s

Match 57: Quarterfinal 1 (Win 49 vs Win 50) : France vs Portugal

History match-up : https://www.11v11.com/teams/france/tab/opposingTeams/opposition/Portugal/

```{r}
m = 5000
set.seed(1602)
fra_gsqf = round(sum(kophase$teamC1_gs[which(kophase$teamC1 == "France")])/(length(kophase$teamC1[which((kophase$teamC1 == "France"))])*6),2)
fra_gcqf = round(sum(kophase$teamC1_gc[which(kophase$teamC1 == "France")])/(length(kophase$teamC1[which((kophase$teamC1 == "France"))])*6),2)
por_gsqf = round(sum(kophase$teamB2_gs[which(kophase$teamB2 == "Portugal")])/(length(kophase$teamB2[which((kophase$teamB2 == "Portugal"))])*6),2)
por_gcqf = round(sum(kophase$teamB2_gc[which(kophase$teamB2 == "Portugal")])/(length(kophase$teamB2[which((kophase$teamB2 == "Portugal"))])*6),2)
match57 = data.frame(team1 = c("France"), team2 = c("Portugal"), played = c(25), fraW = c(18), draw = c(1), porW = c(6), FRA_gsqf = c(48), POR_gsqf = c(28),
                      avggfra_gs = c(fra_gsqf), avggfra_gc = c(fra_gcqf), avggpor_gs = c(por_gsqf), avggpor_gc = c(por_gcqf))
#france gs = cro_gc
avghisfraqf = match57$FRA_gsqf / match57$played
avghisporqf = match57$POR_gsqf / match57$played

resmatch57 = NULL
for(i in 1:m){
resmatch57[i] = list(kophasegoals(as.character(match57$team1), match57$avggfra_gs, match57$avggfra_gc, avghisfraqf, as.character(match57$team2), match57$avggpor_gs, match57$avggpor_gc, avghisporqf))
}
```

Analyze match 57

```{r}
france_win_perqf  = 0
france_gsqf = 0
portugal_win_perqf = 0
portugal_gsqf = 0
for(i in 1:m){
  if(resmatch57[[i]][8] == "France"){ france_win_perqf = france_win_perqf + 1 }
  else{ portugal_win_perqf = portugal_win_perqf + 1 }
  france_gsqf   = france_gsqf  + as.numeric(resmatch57[[i]][2])
  portugal_gsqf = portugal_gsqf + as.numeric(resmatch57[[i]][3])
}
france_win_perqf/m * 100
round(france_gsqf/m,2)
portugal_win_perqf/m * 100
round(portugal_gsqf/m,2)
```

France 3 - 2 Portugal

Match 58: Quarterfinal 2 (Win 53 vs Win 54): Brazil vs Belgium
History match-up : https://www.11v11.com/teams/brazil/tab/opposingTeams/opposition/Belgium/

```{r}
set.seed(1602)
bra_gsqf = round(sum(kophase$teamE1_gs[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
bra_gcqf = round(sum(kophase$teamE1_gc[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
bel_gsqf = round(sum(kophase$teamG1_gs[which(kophase$teamG1 == "Belgium")])/(length(kophase$teamG1[which((kophase$teamG1 == "Belgium"))])*6),2)
bel_gcqf = round(sum(kophase$teamG1_gc[which(kophase$teamG1 == "Belgium")])/(length(kophase$teamG1[which((kophase$teamG1 == "Belgium"))])*6),2)
match58 = data.frame(team1 = c("Brazil"), team2 = c("Mexico"), played = c(4), bragW = c(3), draw = c(0), belW = c(1), BRA_gsqf = c(9), BEL_gsqf = c(6),
                      avggbra_gs = c(bra_gsqf), avggbra_gc = c(bra_gcqf), avggbel_gs = c(bel_gsqf), avggbel_gc = c(bel_gcqf))

#Brazil gs = Mexico gc
avghisbraqf = match58$BRA_gsqf / match58$played
avghisbelqf = match58$BEL_gsqf / match58$played

resmatch58 = NULL
for(i in 1:m){
resmatch58[i] = list(kophasegoals(as.character(match58$team1), match58$avggbra_gs, match58$avggbra_gc, avghisbraqf, as.character(match58$team2), match58$avggbel_gs, match58$avggbel_gc, avghisbelqf))
}
```

Analyze match 58

```{r}
brazil_win_perqf  = 0
brazil_gsqf = 0
belgium_win_perqf = 0
belgium_gsqf = 0

for(i in 1:m){
  if(resmatch58[[i]][8] == "Brazil"){ brazil_win_perqf = brazil_win_perqf + 1 }
  else{ belgium_win_perqf = belgium_win_perqf + 1 }
  brazil_gsqf = brazil_gsqf  + as.numeric(resmatch58[[i]][2])
  belgium_gsqf = belgium_gsqf + as.numeric(resmatch58[[i]][3])
}
brazil_win_perqf/m * 100
round(brazil_gsqf/m ,2)
belgium_win_perqf/m * 100
round(belgium_gsqf/m, 2)
```

Brazil 3 - 2 Belgium

Match 59: Quarterfinal 3 (Win 55 vs Win 56): Germany vs England
History match-up : https://www.11v11.com/teams/germany/tab/opposingTeams/opposition/England/

```{r}
set.seed(1602)
ger_gsqf = round(sum(kophase$teamF1_gs[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)
ger_gcqf = round(sum(kophase$teamF1_gc[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)
eng_gsqf = round(sum(kophase$teamG2_gs[which(kophase$teamG2 == "England")])/(length(kophase$teamG2[which((kophase$teamG2 == "England"))])*6),2)
eng_gcqf = round(sum(kophase$teamG2_gc[which(kophase$teamG2 == "England")])/(length(kophase$teamG2[which((kophase$teamG2 == "England"))])*6),2)
match59 = data.frame(team1 = c("Germany"), team2 = c("England"), played = c(32), gergW = c(15), draw = c(4), engW = c(13), GER_gs = c(40), ENG_gs = c(53),
                      avggger_gs = c(ger_gsqf), avggger_gc = c(ger_gcqf), avggeng_gs = c(eng_gsqf), avggeng_gc = c(eng_gcqf))

#Belgium gs = Colombia gc
avghisgerqf = match59$GER_gs / match59$played
avghisengqf = match59$ENG_gs / match59$played

resmatch59 = NULL
for(i in 1:m){
resmatch59[i] = list(kophasegoals(as.character(match59$team1), match59$avggger_gs, match59$avggger_gc, avghisgerqf, as.character(match59$team2), match59$avggeng_gs, match59$avggeng_gc, avghisengqf))
}
```

Analyze match 59

```{r}
germany_win_perqf  = 0
germany_gsqf = 0
england_win_perqf = 0
england_gsqf = 0

for(i in 1:m){
  if(resmatch59[[i]][8] == "Germany"){ germany_win_perqf = germany_win_perqf + 1 }
  else{ england_win_perqf = england_win_perqf + 1 }
  germany_gsqf = germany_gsqf + as.numeric(resmatch59[[i]][2])
  england_gsqf = england_gsqf + as.numeric(resmatch59[[i]][3])
}
germany_win_perqf/m * 100
round(germany_gsqf /m,2)
england_win_perqf/m * 100
round(england_gsqf /m, 2)
```

Germany 2 - 2 England (Germany win on penalty)

Match 60: Quarterfinal 4 (Win 51 vs Win 52): Spain vs Argentina
History match-up : https://www.11v11.com/teams/spain/tab/opposingTeams/opposition/Argentina/

```{r}
set.seed(1602)
esp_gsqf = round(sum(kophase$teamB1_gs[which(kophase$teamB1 == "Spain")])/(length(kophase$teamB1[which((kophase$teamB1 == "Spain"))])*6),2)
esp_gcqf = round(sum(kophase$teamB1_gc[which(kophase$teamB1 == "Spain")])/(length(kophase$teamB1[which((kophase$teamB1 == "Spain"))])*6),2)
arg_gsqf = round(sum(kophase$teamD1_gs[which(kophase$teamD1 == "Argentina")])/(length(kophase$teamD1[which((kophase$teamD1 == "Argentina"))])*6),2)
arg_gcqf = round(sum(kophase$teamD1_gc[which(kophase$teamD1 == "Argentina")])/(length(kophase$teamD1[which((kophase$teamD1 == "Argentina"))])*6),2)
match60 = data.frame(team1 = c("Spain"), team2 = c("Argentina"), played = c(14), espW = c(6), draw = c(2), argW = c(6), ESP_gs = c(19), ARG_gs = c(18),
                      avggesp_gs = c(esp_gsqf), avggesp_gc = c(esp_gcqf), avggarg_gs = c(arg_gsqf), avggarg_gc = c(arg_gcqf))

#Spain gs = Russia gc
avghisespqf = match60$ESP_gs / match60$played
avghisargqf = match60$ARG_gs / match60$played

resmatch60 = NULL
for(i in 1:m){
resmatch60[i] = list(kophasegoals(as.character(match60$team1), match60$avggesp_gs, match60$avggesp_gc, avghisespqf, as.character(match60$team2), match60$avggarg_gs, match60$avggarg_gc, avghisargqf))
}
```

Analyze match 60

```{r}
spain_win_perqf  = 0
spain_gsqf = 0
argentina_win_perqf = 0
argentina_gsqf = 0
for(i in 1:m){
  if(resmatch60[[i]][8] == "Spain"){ spain_win_perqf = spain_win_perqf + 1 }
  else{ argentina_win_perqf = argentina_win_perqf + 1 }
  spain_gsqf  = spain_gsqf  + as.numeric(resmatch60[[i]][2])
  argentina_gsqf = argentina_gsqf + as.numeric(resmatch60[[i]][3])
}
spain_win_perqf/m * 100
round(spain_gsqf/m ,2)
argentina_win_perqf/m * 100
round(argentina_gsqf/m, 2)
```

Spain 2 - 2 Argentina (Spain win on penalty)

Semifinals 1  (Win 57 vs Win 58): France vs Brazil
Match-up: https://www.11v11.com/teams/france/tab/opposingTeams/opposition/Brazil/
```{r}
m = 5000
set.seed(1602)
fra_gssf = round(sum(kophase$teamC1_gs[which(kophase$teamC1 == "France")])/(length(kophase$teamC1[which((kophase$teamC1 == "France"))])*6),2)
fra_gcsf = round(sum(kophase$teamC1_gc[which(kophase$teamC1 == "France")])/(length(kophase$teamC1[which((kophase$teamC1 == "France"))])*6),2)
bra_gssf = round(sum(kophase$teamE1_gs[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
bra_gcsf = round(sum(kophase$teamE1_gc[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
match61 = data.frame(team1 = c("France"), team2 = c("Brazil"), played = c(15), fraW = c(6), draw = c(3), braW = c(6), FRA_gs = c(18), BRA_gs = c(24),
                      avggfra_gs = c(fra_gssf), avggfra_gc = c(fra_gcsf), avggbra_gs = c(bra_gssf), avggbra_gc = c(bra_gcsf))
#france gs = cro_gc
avghisfrasf = match61$FRA_gs / match61$played
avghisbrasf = match61$BRA_gs / match61$played

resmatch61 = NULL
for(i in 1:m){
resmatch61[i] = list(kophasegoals(as.character(match61$team1), match61$avggfra_gs, match61$avggfra_gc, avghisfrasf, as.character(match61$team2), match61$avggbra_gs, match61$avggbra_gc, avghisbrasf))
}
```

Analyze match 61

```{r}
france_win_persf  = 0
france_gssf = 0
brazil_win_persf = 0
brazil_gssf = 0
for(i in 1:m){
  if(resmatch61[[i]][8] == "France"){ france_win_persf = france_win_persf + 1 }
  else{ brazil_win_persf = brazil_win_persf + 1 }
  france_gssf  = france_gssf  + as.numeric(resmatch61[[i]][2])
  brazil_gssf = brazil_gssf + as.numeric(resmatch61[[i]][3])
}
france_win_persf/m * 100
round(france_gssf/m,2)
brazil_win_persf/m * 100
round(brazil_gssf/m,2)
```

France 2 - 2 Brazil : Brazil win on penalty
Semifinals 1  (Win 59 vs Win 60): Germany vs Spain
Matchup : https://www.11v11.com/teams/germany/tab/opposingTeams/opposition/Spain/

```{r}
set.seed(1602)
ger_gssf = round(sum(kophase$teamF1_gs[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)
ger_gcsf = round(sum(kophase$teamF1_gc[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)
esp_gssf = round(sum(kophase$teamB1_gs[which(kophase$teamB1 == "Spain")])/(length(kophase$teamB1[which((kophase$teamB1 == "Spain"))])*6),2)
esp_gcsf = round(sum(kophase$teamB1_gc[which(kophase$teamB1 == "Spain")])/(length(kophase$teamB1[which((kophase$teamB1 == "Spain"))])*6),2)
match62 = data.frame(team1 = c("Germany"), team2 = c("Spain"), played = c(23), gergW = c(9), draw = c(7), espW = c(7), GER_gs = c(29), ESP_gs = c(24),
                      avggger_gs = c(ger_gssf), avggger_gc = c(ger_gcsf), avggesp_gs = c(esp_gssf), avggesp_gc = c(esp_gcsf))

#Belgium gs = Colombia gc
avghisgersf = match62$GER_gs / match62$played
avghisespsf = match62$ESP_gs / match62$played

resmatch62 = NULL
for(i in 1:m){
resmatch62[i] = list(kophasegoals(as.character(match62$team1), match62$avggger_gs, match62$avggger_gc, avghisgersf, as.character(match62$team2), match62$avggesp_gs, match62$avggesp_gc, avghisespsf))
}
```

Analyze match 59

```{r}
germany_win_persf  = 0
germany_gssf = 0
spain_win_persf = 0
spain_gssf = 0

for(i in 1:m){
  if(resmatch62[[i]][8] == "Germany"){ germany_win_persf = germany_win_persf + 1 }
  else{ spain_win_persf = spain_win_persf + 1 }
  germany_gssf = germany_gssf + as.numeric(resmatch62[[i]][2])
  spain_gssf = spain_gssf + as.numeric(resmatch62[[i]][3])
}
germany_win_persf/m * 100
round(germany_gssf/m,2)
spain_win_persf/m * 100
round(spain_gssf/m, 2)
```
Germany 2 - 2 Spain Germany win on penalty

Finals Brazil vs Germany
```{r}
m = 5000
set.seed(1602)
bra_gsf = round(sum(kophase$teamE1_gs[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
bra_gcf = round(sum(kophase$teamE1_gc[which(kophase$teamE1 == "Brazil")])/(length(kophase$teamE1[which((kophase$teamE1 == "Brazil"))])*6),2)
ger_gsf = round(sum(kophase$teamF1_gs[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)
ger_gcf = round(sum(kophase$teamF1_gc[which(kophase$teamF1 == "Germany")])/(length(kophase$teamF1[which((kophase$teamF1 == "Germany"))])*6),2)

match64 = data.frame(team1 = c("Brazil"), team2 = c("Germany"), played = c(23), braW = c(13), draw = c(5), gerW = c(5), BRA_gs = c(41), GER_gs = c(31),
                      avggbra_gs = c(bra_gsf), avggbra_gc = c(bra_gcf), avggger_gs = c(ger_gsf), avggger_gc = c(ger_gcf))
#france gs = cro_gc
avghisbraf = match64$BRA_gs / match64$played
avghisgerf = match64$GER_gs / match64$played

resmatch64 = NULL
for(i in 1:m){
resmatch64[i] = list(kophasegoals(as.character(match64$team1), match64$avggbra_gs, match64$avggbra_gc, avghisbraf, as.character(match64$team2), match64$avggger_gs, match64$avggger_gc, avghisgerf))
}
```

Analyze match 61

```{r}
brazil_win_perf = 0
brazil_gsf = 0
germany_win_perf = 0
germany_gsf = 0
for(i in 1:m){
  if(resmatch61[[i]][8] == "Brazil"){ brazil_win_perf = brazil_win_perf + 1 }
  else{ germany_win_perf = germany_win_perf + 1 }
  brazil_gsf  = brazil_gsf  + as.numeric(resmatch61[[i]][2])
  germany_gsf = germany_gsf + as.numeric(resmatch61[[i]][3])
}
brazil_win_perf/m * 100
round(brazil_gsf/m,2)
germany_win_perf/m * 100
round(germany_gsf/m,2)
```


Summary: All the draw result might be different

1/16
France       3 - 1    Croatia    
Uruguay      1 - 2    Portugal
Brazil       4 - 1    Mexico 
Belgium(W)   2 - 2    Colombia 


Spain        4 - 2    Russia
Argentina(W) 2 - 2    Denmark
Germany      4 - 2    Switzerland
Poland       2 - 1    England

Quarterfinals:
France       3 - 2    Portugal
Brazil       3 - 2    Belgium

Spain(W)     2 - 2    Argentina
Germany(W)   2 - 2    England

Semifinals:
France       2 - 2    Brazil(W)
Spain(W)     2 - 2    Germany

Finals:
Brazil(W)    2 - 2    Germany