---
title: "World Cup 2018 knock_outphase prediction"
author: "Khuong Le"
output: html_document
---

```{r}
pkg_list = c("ggplot2", "stringr", "rvest", "tidyr", "dplyr", "base","scales","plyr", "reshape2")
mia_pkgs = pkg_list[!(pkg_list %in% installed.packages()[,"Package"])]
if(length(mia_pkgs) > 0) install.packages(mia_pkgs)
loaded_pkgs = lapply(pkg_list, require, character.only=TRUE)
```

The data below is the result from predictwc2018.Rmd file. From this data we will calculate the probability to advance next ground for each team.  
```{r}
kophase = read.csv("ko.csv")
#kophase
```
 
GroupA:

```{r}
advrus1   = round(length(kophase$teamA1[which(kophase$teamA1 == "Russia")]) / (length(kophase$teamA1)), 4)*100
advuru1   = round(length(kophase$teamA1[which(kophase$teamA1 == "Uruguay")]) / (length(kophase$teamA1)),4)*100 
advegy1   = round(length(kophase$teamA1[which(kophase$teamA1 == "Egypt")]) / (length(kophase$teamA1)),4)*100 
advksa1   = round(length(kophase$teamA1[which(kophase$teamA1 == "Saudi Arabia")]) / (length(kophase$teamA1)),4)*100 

advrus2   = round(length(kophase$teamA2[which(kophase$teamA2 == "Russia")]) / (length(kophase$teamA1)),4)*100 
advuru2   = round(length(kophase$teamA2[which(kophase$teamA2 == "Uruguay")]) / (length(kophase$teamA1)),4)*100 
advegy2   = round(length(kophase$teamA2[which(kophase$teamA2 == "Egypt")]) / (length(kophase$teamA1)),4)*100  
advksa2   = round(length(kophase$teamA2[which(kophase$teamA2 == "Saudi Arabia")]) / (length(kophase$teamA1)),4)*100 

gadata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("Egypt", "Russia", "Saudi Arabia", "Uruguay"),2),
        percentage = c(advegy1, advrus1, advksa1, advuru1, advegy2, advrus2, advksa2, advuru2))

gA = ggplot(data = gadata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)
jpeg('gA.jpg')
plot(gA)
```

Uruguay     : has `r (advuru1 + advuru2)` % advance to next round

Russia      : has `r (advrus1 + advrus2)` % advance to next round

Egypt       : has `r (advegy1 + advegy2)` % advance to next round

Saudi Arabia: has `r (advksa1 + advksa2)` % advance to next round


Group B:

```{r}
advpor1   = round(length(kophase$teamB1[which(kophase$teamB1 == "Portugal")])/ (length(kophase$teamB1)), 4)*100
advesp1   = round(length(kophase$teamB1[which(kophase$teamB1 == "Spain")])/ (length(kophase$teamB1)), 4)*100
advmar1   = round(length(kophase$teamB1[which(kophase$teamB1 == "Morocco")])/ (length(kophase$teamB1)), 4)*100
adviri1   = round(length(kophase$teamB1[which(kophase$teamB1 == "Iran")])/ (length(kophase$teamB1)), 4)*100

advpor2   = round(length(kophase$teamB1[which(kophase$teamB2 == "Portugal")])/ (length(kophase$teamB2)), 4)*100
advesp2   = round(length(kophase$teamB1[which(kophase$teamB2 == "Spain")])/ (length(kophase$teamB2)), 4)*100
advmar2   = round(length(kophase$teamB1[which(kophase$teamB2 == "Morocco")])/ (length(kophase$teamB2)), 4)*100
adviri2   = round(length(kophase$teamB1[which(kophase$teamB2 == "Iran")])/ (length(kophase$teamB2)), 4)*100

gbdata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("Portugal", "Spain", "Morocco", "Iran"),2),
        percentage = c(advpor1, advesp1, advmar1, adviri1, advpor2, advesp2, advmar2, adviri2))

gB = ggplot(data = gbdata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)
jpeg('gB.jpg')
plot(gB)
```

Portugual : has `r (advpor1 + advpor2)` % advance to next round

Spain     : has `r (advesp1 + advesp2)` % advance to next round

Morocco   : has `r (advmar1 + advmar2)` % advance to next round

Iran      : has `r (adviri1 + adviri2)` % advance to next round

Group C:

```{r}
advfra1   = round(length(kophase$teamC1[which(kophase$teamC1 == "France")])/ (length(kophase$teamC1)), 4)*100
advper1   = round(length(kophase$teamC1[which(kophase$teamC1 == "Peru")])/ (length(kophase$teamC1)), 4)*100
advdan1   = round(length(kophase$teamC1[which(kophase$teamC1 == "Denmark")])/ (length(kophase$teamC1)), 4)*100
advaus1   = round(length(kophase$teamC1[which(kophase$teamC1 == "Australia")])/ (length(kophase$teamC1)), 4)*100

advfra2   = round(length(kophase$teamC2[which(kophase$teamC2 == "France")])/ (length(kophase$teamC2_gs)), 4)*100
advper2   = round(length(kophase$teamC2[which(kophase$teamC2 == "Peru")])/ (length(kophase$teamC2_gs)), 4)*100
advdan2   = round(length(kophase$teamC2[which(kophase$teamC2 == "Denmark")])/ (length(kophase$teamC2_gs)), 4)*100
advaus2   = round(length(kophase$teamC2[which(kophase$teamC2 == "Australia")])/ (length(kophase$teamC2_gs)), 4)*100

gcdata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("France", "Peru", "Denmark", "Australia"),2),
        percentage = c(advfra1, advper1, advdan1, advaus1, advfra2, advper2, advdan2, advaus2))

gC = ggplot(data = gcdata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)

jpeg('gC.jpg')
plot(gC)
```

France    : has `r (advfra1 + advfra2)` % advance to next round

Peru      : has `r (advper1 + advper2)` % advance to next round

Denmark   : has `r (advdan1 + advdan2)` % advance to next round

Australia : has `r (advaus1 + advaus2)` % advance to next round

Seed in group D: 

```{r}
advarg1   = round(length(kophase$teamD1[which(kophase$teamD1 == "Argentina")])/ (length(kophase$teamD1_gs)), 4)*100
advice1   = round(length(kophase$teamD1[which(kophase$teamD1 == "Iceland")])/(length(kophase$teamD1_gs)), 4)*100
advcro1   = round(length(kophase$teamD1[which(kophase$teamD1 == "Croatia")])/(length(kophase$teamD1_gs)), 4)*100
advnga1   = round(length(kophase$teamD1[which(kophase$teamD1 == "Nigeria")])/(length(kophase$teamD1_gs)), 4)*100

advarg2   = round(length(kophase$teamD2[which(kophase$teamD2 == "Argentina")])/ (length(kophase$teamD2_gs)), 4)*100
advice2   = round(length(kophase$teamD2[which(kophase$teamD2 == "Iceland")])/ (length(kophase$teamD2_gs)), 4)*100
advcro2   = round(length(kophase$teamD2[which(kophase$teamD2 == "Croatia")])/ (length(kophase$teamD2_gs)), 4)*100
advnga2   = round(length(kophase$teamD2[which(kophase$teamD2 == "Nigeria")])/ (length(kophase$teamD2_gs)), 4)*100

gddata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("Argentina", "Iceland", "Croatia", "Nigeria"),2),
        percentage = c(advarg1, advice1, advcro1, advnga1, advarg2, advice2, advcro2, advnga2))

gD = ggplot(data = gddata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)
jpeg('gD.jpg')
plot(gD)
```

Argentina : has `r (advarg1 + advarg2)` % advance to next round

Iceland   : has `r (advice1 + advice2)` % advance to next round

Croatia   : has `r (advcro1 + advcro2)` % advance to next round

Nigeria   : has `r (advnga1 + advnga2)` % advance to next round

Group E: 

```{r}
advbra1   = round(length(kophase$teamE1[which(kophase$teamE1 == "Brazil")])/ (length(kophase$teamE1_gs)), 4)*100
advswi1   = round(length(kophase$teamE1[which(kophase$teamE1 == "Switzerland")])/ (length(kophase$teamE1_gs)), 4)*100
advcri1   = round(length(kophase$teamE1[which(kophase$teamE1 == "Costa Rica")])/ (length(kophase$teamE1_gs)), 4)*100
advsrb1   = round(length(kophase$teamE1[which(kophase$teamE1 == "Serbia")])/ (length(kophase$teamE1_gs)), 4)*100

advbra2   = round(length(kophase$teamE2[which(kophase$teamE2 == "Brazil")])/ (length(kophase$teamE2_gs)), 4)*100
advswi2   = round(length(kophase$teamE2[which(kophase$teamE2 == "Switzerland")])/ (length(kophase$teamE2_gs)), 4)*100
advcri2   = round(length(kophase$teamE2[which(kophase$teamE2 == "Costa Rica")])/ (length(kophase$teamE2_gs)), 4)*100
advsrb2   = round(length(kophase$teamE2[which(kophase$teamE2 == "Serbia")])/ (length(kophase$teamE2_gs)), 4)*100

gedata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("Brazil", "Switzerland", "Costa Rica", "Serbia"),2),
        percentage = c(advbra1, advswi1, advcri1, advsrb1, advbra2, advswi2,  advcri2, advsrb2))

gE = ggplot(data = gedata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)
jpeg('gE.jpg')
plot(gE)
```

Brazil      : has `r (advbra1 + advbra2)` % advance to next round

Switzerland : has `r (advswi1 + advswi2)` % advance to next round

Costa Rica  : has `r (advcri1 + advcri2)` % advance to next round

Serbia      : has `r (advsrb1 + advsrb2)` % advance to next round

Group F: 

```{r}
advger1   = round(length(kophase$teamF1[which(kophase$teamF1 == "Germany")])/ (length(kophase$teamF1_gs)), 4)*100
advmex1   = round(length(kophase$teamF1[which(kophase$teamF1 == "Mexico")])/ (length(kophase$teamF1_gs)), 4)*100
advswe1   = round(length(kophase$teamF1[which(kophase$teamF1 == "Sweden")])/ (length(kophase$teamF1_gs)), 4)*100
advkor1   = round(length(kophase$teamF1[which(kophase$teamF1 == "South Korea")])/ (length(kophase$teamF1_gs)), 4)*100

advger2   = round(length(kophase$teamF2[which(kophase$teamF2 == "Germany")])/ (length(kophase$teamF2_gs)), 4)*100
advmex2   = round(length(kophase$teamF2[which(kophase$teamF2 == "Mexico")])/ (length(kophase$teamF2_gs)), 4)*100
advswe2   = round(length(kophase$teamF2[which(kophase$teamF2 == "Sweden")])/ (length(kophase$teamF2_gs)), 4)*100
advkor2   = round(length(kophase$teamF2[which(kophase$teamF2 == "South Korea")])/ (length(kophase$teamF2_gs)), 4)*100

gfdata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("Germany", "Mexico", "Sweden", "South Korea"),2),
        percentage = c(advger1, advmex1, advswe1, advkor1, advger2, advmex2, advswe2, advkor2))

gF = ggplot(data = gfdata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)
jpeg('gF.jpg')
plot(gF)
```

Germany     : has `r (advger1 + advger2)` % advance to next round

Mexico      : has `r (advmex1 + advmex2)` % advance to next round

Sweden      : has `r (advswe1 + advswe2)` % advance to next round

South Korea : has `r (advkor1 + advkor2)` % advance to next round

Group G: 

```{r}
advbel1   = round(length(kophase$teamG1[which(kophase$teamG1 == "Belgium")])/ (length(kophase$teamG1_gs)), 4)*100
adveng1   = round(length(kophase$teamG1[which(kophase$teamG1 == "England")])/ (length(kophase$teamG1_gs)), 4)*100
advtun1   = round(length(kophase$teamG1[which(kophase$teamG1 == "Tunisia")])/ (length(kophase$teamG1_gs)), 4)*100
advpan1   = round(length(kophase$teamG1[which(kophase$teamG1 == "Panama")])/ (length(kophase$teamG1_gs)), 4)*100

advbel2   = round(length(kophase$teamG2[which(kophase$teamG2 == "Belgium")])/ (length(kophase$teamG2_gs)), 4)*100
adveng2   = round(length(kophase$teamG2[which(kophase$teamG2 == "England")])/ (length(kophase$teamG2_gs)), 4)*100
advtun2   = round(length(kophase$teamG2[which(kophase$teamG2 == "Tunisia")])/ (length(kophase$teamG2_gs)), 4)*100
advpan2   = round(length(kophase$teamG2[which(kophase$teamG2 == "Panama")])/ (length(kophase$teamG2_gs)), 4)*100

ggdata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("Belgium", "England", "Tunisia", "Panama"),2),
        percentage = c(advbel1, adveng1, advtun1, advpan1, advbel2, adveng2, advtun2, advpan2))

gG = ggplot(data = ggdata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)
jpeg('gA.jpg')
plot(gG)
```

Belgium : has `r (advbel1 + advbel2)` % advance to next round

England : has `r (adveng1 + adveng2)` % advance to next round

Tunisia : has `r (advtun1 + advtun2)` % advance to next round

Panama  : has `r (advpan1 + advpan2)` % advance to next round

Group H: 

```{r}
advpol1   = round(length(kophase$teamH1[which(kophase$teamH1 == "Poland")])/ (length(kophase$teamH1_gs)), 4)*100
advsen1   = round(length(kophase$teamH1[which(kophase$teamH1 == "Colombia")])/ (length(kophase$teamH1_gs)), 4)*100
advcol1   = round(length(kophase$teamH1[which(kophase$teamH1 == "Senegal")])/ (length(kophase$teamH1_gs)), 4)*100
advjpn1   = round(length(kophase$teamH1[which(kophase$teamH1 == "Japan")])/ (length(kophase$teamH1_gs)), 4)*100

advpol2   = round(length(kophase$teamH2[which(kophase$teamH2 == "Poland")])/ (length(kophase$teamH2_gs)), 4)*100
advsen2   = round(length(kophase$teamH2[which(kophase$teamH2 == "Colombia")])/ (length(kophase$teamH2_gs)), 4)*100
advcol2   = round(length(kophase$teamH2[which(kophase$teamH2 == "Senegal")])/ (length(kophase$teamH2_gs)), 4)*100
advjpn2   = round(length(kophase$teamH2[which(kophase$teamH2 == "Japan")])/ (length(kophase$teamH2_gs)), 4)*100

ghdata  = data.frame(
        pos        = rep(c("First", "Second"), each=4),
        country    = rep(c("Poland", "Colombia", "Senegal", "Japan"),2),
        percentage = c(advpol1, advsen1, advcol1, advjpn1, advpol2, advsen2, advcol2, advjpn2))

gH = ggplot(data = ghdata, aes(x = country, y = percentage, fill = pos)) + 
    geom_bar(stat = "identity", position=position_dodge()) +  
    geom_text(aes(label = percentage), position = position_dodge(0.95), vjust=0.5, color = "darkred", size = 3)

jpeg('gH.jpg')
plot(gH)
```

Poland   : has `r (advpol1 + advpol2)` % advance to next round

Colombia : has `r (advsen1 + advsen2)` % advance to next round

Senegal  : has `r (advcol1 + advcol2)` % advance to next round

Japan    : has `r (advjpn1 + advjpn2)` % advance to next round
